---
title: "Aides Drug"
author: "John!"
date: "Spring 23"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
triUmp <-read.csv(file="triUmpsal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides drug (triUmpsal) is under test in clinical trials. Consider only the DrugUsers, does this drug seem effective?  Hint - use dplyr to obtain that subpopulation with the filter command.

```{r}
druggies <- filter(triUmp, DrugUser=="yes")
```


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~treatment + infected,data=druggies)
barchartGC(~treatment + infected,data=druggies, type="percent")

```

```{r}
barchartGC(~infected + treatment,data=druggies)
barchartGC(~infected + treatment,data=druggies, type="percent")

```

Interestingly the difference in this study is that the there is a box defined as "aids" and a second box labeled "none". The study communicates that there was about a substantial amount of people in the first box who did not get aids because of a drug and there was a substantial amount of people who did get aids in the second group "none" because of a placebo effect.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~infected + treatment, data=druggies)
rowPerc(table1)
colPerc(table1)
```

Interestingly the study communicates columns and rows representing the study of this clinical trial that took care of patients who were diagnosed with aids. In the row percents it is an explanation on the diagnostics of patients with aids and in the column it is informing the reader about the involvement of a drug or placebo.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Interestingly a number close to zero that is 0.0000000423 can be read in the p-value on a "chi-square" test. Next there is also a "fisher's" test further communicating the chances on the overall study, according to this test there are odds of 0.35.     

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

First this write up began with the the introduction to patients of aids who used a drug in relationship to relieve them from the illness. Next we identified different measurements and were able to identify that patients who were using a drug were really being relieved. Lastly this proves that the drugs were effective.  


 
 